Thermal reactionome of a temperate ant species

### 2014-05-16 doc/ApTranscriptome_manuscript.Rmd
Updates to Results and starting on Discussion

**Table 1 and Figure 1 are redundant - which is preferable??**

```{r expression_type_plot, echo=FALSE, fig.cap = "Mosaic plot that shows the proportion of thermally-responsive genes in each expression category for each species."}
mosaicplot(t(tt2), shade = FALSE, ylab = "A. carolinensis", xlab = "A. picea", main = "", cex = 0.5)
```

@@

@@

>>>>

We performed a number of comparisons to evaluate the extent to which the thermal reactionomes differed between *A. carolinensis* and *A. picea*. First, we found that the temperature of maximum expression for the thermally-responsive genes differed between species (Figure 3), with a similar number of genes with maximum expression at high temperatures, many more genes with maximum expression at intermediate temperatures in *A. carolinensis* and more genes with maximum expression at low temperatures in *A. picea*.

@@

### Molecular comparisons

@@

- greater adaptability to cold than hot thermal stress
    - *A. carolinensis* limited future potential to adapt to heat stress
- different mechanisms of thermal tolernace
    - *A. carolinensis* tolerates thermal stress by shutting down (*Intermediate* genes)
    - *A. picea* tolerates by a combination of shutting down and activating 'protective' genes 
       - some indication that *A. picea* maintains express in cold conditions that *A. carolinensis* shuts down based on overlap of *Low* genes in *A. picea* with *Intermediate* genes in *A. carolinensis*
- metabolic compensation?

-------------------------------------
